A Linked Open Social Database for Scientific Benchmarking

### 2016-08-01 paper.tex
add of directions from chu

\section{Introduction}
In recent years, the web of linked data~\cite{lee1} has attracted wide attention in
both research and application realms.
However, there is a lack of datasets for benchmarking results,
specially in the complex networks field, yielding diverse results from 
poorly related data.

@@

This work presents a linked open social database (LOSD) with diverse
provenance, including Facebook, Twitter, IRC, Email and detached
instances.
Such data is proposed as a common repertoire for scientific
research involving networks and textual content.

>>>>

\section{Introduction}

% In recent years, the web of linked data~\cite{lee1} has attracted wide attention in
% both research and application realms.
Open machine-readable contents and tools are desired
in performing knowledge discovery in social data,
% there is a lack of datasets for benchmarking results,
However, there is a lack of datasets for benchmarking results,
specially associated the complex networks field,
yielding diverse results from poorly related sources.

@@

This work presents a framework that provides machine-readable contents with a
database on social networks.
This has been made by linkng social data into an open social database with diverse
provenance, including Facebook, Twitter, IRC, Email and detached
instances.
Such data is proposed as a common repertoire for scientific
research involving networks and textual content and may be extended.
